Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-15 talk/pepm2011/paper.tex
make the paper sort of presentable

There exists a large number of works on escape analysis, which is a program
analysis that tries to find an upper bound for the lifetime of objects allocated
at specific program points
\cite{goldberg_higher_1990,park_escape_1992,choi_escape_1999,bruno_blanchet_escape_2003}.
This information can then be used to decide that certain objects can be
allocated on the stack, because their lifetime does not exceed that of the stack
frame it is allocated in. The difference to our work is that escape analysis is
split into an analysis and an optimization phase. The analysis can be a lot more
complex than our simple one-pass optimization. Also, stack-allocation reduces
garbage-collection pressure but does not optimize away the actual accesses to
the stack-allocated object. In our case, an object is not needed at all any
more.
XXX more papers?

@@

partial evaluation:

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{Mogensen:PEPM93}.)

@@

xxx: 
Other related work is compile-time garbage collection \cite{mazur_practical_2001}, which
tries to ....;
  separation logic
  %; John Hughes: type specialization

>>>>

There exists a large number of works on escape analysis, which is a program
analysis that tries to find an upper bound for the lifetime of objects allocated
at specific program points
\cite{goldberg_higher_1990,park_escape_1992,choi_escape_1999,bruno_blanchet_escape_2003}.
This information can then be used to decide that certain objects can be
allocated on the stack, because their lifetime does not exceed that of the stack
frame it is allocated in. The difference to our work is that escape analysis is
split into an analysis and an optimization phase. The analysis can be a lot more
complex than our simple one-pass optimization. Also, stack-allocation reduces
garbage-collection pressure but does not optimize away the actual accesses to
the stack-allocated object. In our case, an object is not needed at all any
more.

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{Mogensen:PEPM93}.

@@

%xxx: 
%Other related work is compile-time garbage collection \cite{mazur_practical_2001}, which
%tries to ....;
%  separation logic
  %; John Hughes: type specialization
